A Cloud Native Approach to Adversarial Robustness of Neural Networks

### 2024-03-28 main.tex
update image references

\begin{figure}
  \centering
  % include first image
  \includegraphics[width=0.8\linewidth,trim={20pt 20pt 20pt 20pt},clip]{plots/combined/log_logistic_train_time_partial_effect.pdf}  
  \caption{The partial effect of the training time on the survival time across all datasets and models according to the function $S(t)$ as outlined in Section~\ref{survival_time}. The dotted line represents the baseline survival function $S_{ben}$.}
  \label{fig:partial_effect_train_time}
\end{figure}

@@

\begin{figure}
  \centering
  % include second image
  \includegraphics[width=0.8\linewidth,trim={20pt 20pt 20pt 20pt},clip]{plots/combined/log_logistic_accuracy_partial_effect.pdf} 
  \caption{The partial effect of the accuracy on the survival time across all datasets and models according to the function $S(t)$ as outlined in Section~\ref{survival_time}. The dotted line represents the baseline survival function $S_{ben}$.}
  \label{fig:partial_effect_accuracy}
\end{figure}

\begin{figure}
  \centering
  % include second image
  \includegraphics[width=0.8\linewidth,trim={20pt 20pt 20pt 20pt},clip]{plots/combined/log_logistic_adv_failure_rate_partial_effect.pdf} 
  \caption{TODO: replace this with epochs and batch size}
  \label{fig:partial_effect_adv_failure_rate}
\end{figure}

>>>>

% \begin{figure}
%   \centering
%   % include first image
%   \includegraphics[width=0.8\linewidth,trim={20pt 20pt 20pt 20pt},clip]{plots/combined/log_logistic_train_time_partial_effect.pdf}  
%   \caption{The partial effect of the training time on the survival time across all datasets and models according to the function $S(t)$ as outlined in Section~\ref{survival_time}. The dotted line represents the baseline survival function $S_{ben}$.}
%   \label{fig:partial_effect_train_time}
% \end{figure}

@@

\begin{figure}
  \centering
  % include second image
  \includegraphics[width=0.8\linewidth,trim={20pt 20pt 20pt 20pt},clip]{plots/combined/log_logistic_epochs_partial_effect.pdf} 
  \caption{The partial effect of the accuracy on the survival time across all datasets and models according to the function $S(t)$ as outlined in Section~\ref{survival_time}. The dotted line represents the baseline survival function $S_{ben}$.}
  \label{fig:partial_effect_epochs}
\end{figure}

\begin{figure}
  \centering
  % include second image
  \includegraphics[width=0.8\linewidth,trim={20pt 20pt 20pt 20pt},clip]{plots/combined/log_logistic_batch_size_partial_effect.pdf} 
  \caption{TODO: replace this with epochs and batch size}
  \label{fig:partial_effect_batch_size}
\end{figure}

### 2024-03-28 plots/cifar/aft_comparison.tex
update image references

\begin{table}
\caption{Comparison of AFR Models on the CIFAR dataset.}
\label{tab:cifar}
\begin{tabular}{llrrlrr}
\toprule
 & AIC & Concordance for $x_t$ & Concordance for $x_i$ & BIC & Mean $S(t;\theta|x_{t})$ & Mean $S(t;\theta|x_{i})$ \\
\midrule
weibull & -1292.89 & 0.79 & 0.80 & -1292.89 & 0.20 & 0.67 \\
cox & -- & 0.80 & 0.80 & -- & 0.12 & 0.11 \\
log_logistic & -1474.32 & 0.79 & 0.79 & -1474.32 & 0.17 & 0.20 \\
log_normal & -1459.29 & 0.79 & 0.79 & -1459.29 & 0.18 & 0.21 \\
\bottomrule
\end{tabular}
\end{table}

>>>>

\begin{table}
\caption{Comparison of AFR Models on the CIFAR dataset.}
\label{tab:cifar}
\begin{tabular}{llrrlrr}
\toprule
 & AIC & Concordance for $x_t$ & Concordance for $x_i$ & BIC & Mean $S(t;\theta|x_{t})$ & Mean $S(t;\theta|x_{i})$ \\
\midrule
Weibull & -1292.89 & 0.79 & 0.80 & -1292.89 & 0.20 & 0.67 \\
Cox & -- & 0.80 & 0.80 & -- & 0.12 & 0.11 \\
Log Logistic & -1474.32 & 0.79 & 0.79 & -1474.32 & 0.17 & 0.20 \\
Log Normal & -1459.29 & 0.79 & 0.79 & -1459.29 & 0.18 & 0.21 \\
\bottomrule
\end{tabular}
\end{table}

### 2024-03-28 plots/cifar100/aft_comparison.tex
update image references

\begin{table}
\caption{Comparison of AFR Models on the CIFAR100 dataset.}
\label{tab:cifar100}
\begin{tabular}{llrrlrr}
\toprule
 & AIC & Concordance for $x_t$ & Concordance for $x_i$ & BIC & Mean $S(t;\theta|x_{t})$ & Mean $S(t;\theta|x_{i})$ \\
\midrule
weibull & -1159.72 & 0.79 & 0.76 & -1159.72 & 0.21 & 0.21 \\
cox & -- & 0.79 & 0.76 & -- & 0.13 & 0.13 \\
log_logistic & -1313.15 & 0.78 & 0.77 & -1313.15 & 0.20 & 0.20 \\
log_normal & -1299.38 & 0.79 & 0.77 & -1299.38 & 0.20 & 0.20 \\
\bottomrule
\end{tabular}
\end{table}

>>>>

\begin{table}
\caption{Comparison of AFR Models on the CIFAR100 dataset.}
\label{tab:cifar100}
\begin{tabular}{llrrlrr}
\toprule
 & AIC & Concordance for $x_t$ & Concordance for $x_i$ & BIC & Mean $S(t;\theta|x_{t})$ & Mean $S(t;\theta|x_{i})$ \\
\midrule
Weibull & -1159.72 & 0.79 & 0.76 & -1159.72 & 0.21 & 0.21 \\
Cox & -- & 0.79 & 0.76 & -- & 0.13 & 0.13 \\
Log Logistic & -1313.15 & 0.78 & 0.77 & -1313.15 & 0.20 & 0.20 \\
Log Normal & -1299.38 & 0.79 & 0.77 & -1299.38 & 0.20 & 0.20 \\
\bottomrule
\end{tabular}
\end{table}

### 2024-03-28 plots/mnist/aft_comparison.tex
update image references

\begin{table}
\caption{Comparison of AFR Models on the MNIST dataset.}
\label{tab:mnist}
\begin{tabular}{llrrlrr}
\toprule
 & AIC & Concordance for $x_t$ & Concordance for $x_i$ & BIC & Mean $S(t;\theta|x_{t})$ & Mean $S(t;\theta|x_{i})$ \\
\midrule
weibull & -1631.26 & 0.90 & 0.89 & -1631.26 & 0.15 & 0.69 \\
cox & -- & 0.90 & 0.89 & -- & 0.11 & 0.11 \\
log_logistic & -1842.71 & 0.90 & 0.90 & -1842.71 & 0.14 & 0.19 \\
log_normal & -1799.93 & 0.90 & 0.90 & -1799.93 & 0.14 & 0.29 \\
\bottomrule
\end{tabular}
\end{table}

>>>>

\begin{table}
\caption{Comparison of AFR Models on the MNIST dataset.}
\label{tab:mnist}
\begin{tabular}{llrrlrr}
\toprule
 & AIC & Concordance for $x_t$ & Concordance for $x_i$ & BIC & Mean $S(t;\theta|x_{t})$ & Mean $S(t;\theta|x_{i})$ \\
\midrule
Weibull & -1631.26 & 0.90 & 0.89 & -1631.26 & 0.15 & 0.69 \\
Cox & -- & 0.90 & 0.89 & -- & 0.11 & 0.11 \\
Log Logistic & -1842.71 & 0.90 & 0.90 & -1842.71 & 0.14 & 0.19 \\
Log Normal & -1799.93 & 0.90 & 0.90 & -1799.93 & 0.14 & 0.29 \\
\bottomrule
\end{tabular}
\end{table}
